High-order cognition is supported by complex but compressible brain activity patterns

### 2023-02-21 paper/main.tex
i seem to be making backwards progress...but i'm reading some related papers to help frame things and flesh out the intro

Large-scale networks, including the human brain, may be conceptualized as
occupying one or more positions along on a continuum. At one extreme, every
node is fully independent of every other node. At the other extreme, all nodes
are fully coupled and behave identically. Each extreme optimizes key properties
of how the network functions. When every node is independent, the network is
maximally \textit{expressive}: if we define the network's ``state'' as the
total set of activity patterns across nodes, then every state is equally
reachable by a network with fully independent nodes. On the other hand, a fully
coupled network optimizes \textit{robustness}: any subset of nodes, other than
the entire network, may be removed from the network without any loss of
function or expressive power. Note that a given set of nodes might reconfigure
its connections or behaviors under different circumstances to change its
position along this continuum according to the needs at hand. Presumably, most
systems tend to occupy positions between these extremes. We wondered: might
the human brain reconfigure itself to be more flexible or more robust according
to ongoing demands?

@@

Closely related to the above notions of expressiveness versus robustness are
measures of how much \textit{information}~\citep{Shan48} is contained in a
given signal or pattern. Formally, information is defined as the amount of
uncertainty (i.e., entropy) in a given variables' outcomes, measured in
\textit{bits}, or the optimal number of yes/no questions needed to reduce
uncertainty about the variable's outcomes to zero. The \textit{redundancy} of a
signal denotes the difference how expressive the signal could be (i.e.,
proportional to the number of unique states or symbols used to transmit the
signal) and the actual information rate (i.e., the entropy of each individual
state or symbol). If a brain network's nodes are fully independent, then the
number of bits required to express a single activity pattern is proportional to
the number of nodes. The network would also be minimally redundant, since the
status of every node would be needed to fully express a single brain activity
pattern. If a brain network's nodes are fully coupled and identical, then the
number of bits required to express a single activity pattern is proportional to
the number of unique states or values any individual node can take on. Such a
network would be highly redundant, since knowing any individual node's state
would be sufficient to recover the full-brain activity pattern.

>>>>

Large-scale networks, including the human brain, may be conceptualized as
occupying one or more positions along on a continuum. At one extreme, every
node is fully independent of every other node. At the other extreme, all nodes
behave identically. Each extreme optimizes key properties of how the network
functions. When every node is independent, the network is maximally
\textit{expressive}: if we define the network's ``state'' as the activity
pattern across its nodes, then every state is equally reachable by a network
with fully independent nodes. On the other hand, a network of identically
behaved nodes optimizes \textit{robustness}: any subset of nodes may be removed
from the network without any loss of function or expressive power, as long as
any single node remains. Presumably, most natural systems tend to occupy
positions between these extremes. We wondered: might the human brain
reconfigure itself to be more flexible or more robust according to ongoing
demands? In other words, might the brain reconfigure its connections or
behaviors under different circumstances to change its position along this
continuum?

We take as a given that brain activity is highly flexible: our brains can
exhibit nearly infinite activity patterns. However, those activity patterns are
also highly structured. For example, full-brain correlation matrices are stable
within~\citep{FinnEtal15} and across~\citep{YeoEtal11} individuals. This
stability implies that our brains are not

For example, despite stable individual differences in
full-brain correlations~\citep{FinnEtal15},

A number of prior studies suggest that

@@

Closely related to the above notions of expressiveness versus robustness are
measures of how much \textit{information} is contained in a given signal or
pattern, and how \textit{redundant} a signal is. Formally, information is
defined as the amount of uncertainty about a given variables' outcomes (i.e.,
entropy), measured in \textit{bits}, or the optimal number of yes/no questions
needed to reduce uncertainty about the variable's outcomes to zero. Highly
complex systems with many degrees of freedom (i.e., high flexibility and
expressiveness), are more information-rich than simpler or more constrained
systems. The redundancy of a signal denotes the difference how expressive the
signal \textit{could} be (i.e., proportional to the number of unique states or
symbols used to transmit the signal) and the actual information rate (i.e., the
entropy of each individual state or symbol). If a brain network's nodes are
fully independent, then the number of bits required to express a single
activity pattern is proportional to the number of nodes. The network would also
be minimally redundant, since the status of every node would be needed to fully
express a single brain activity pattern. If a brain network's nodes are fully
coupled and identical, then the number of bits required to express a single
activity pattern is proportional to the number of unique states or values any
individual node can take on. Such a network would be highly redundant, since
knowing any individual node's state would be sufficient to recover the
full-brain activity pattern. Highly redundant systems are also robust, since
there is little information loss from losing any given observation.

% Some papers to add in:

% https://www.nature.com/articles/s41467-019-13930-8
% https://onlinelibrary.wiley.com/doi/full/10.1002/jnr.24316?casa_token=PjnffsBh3vgAAAAA%3AynPc_easF6EXPrEK7ihnQ6Jc8QeWq6x0u-ytDsMwxQ4a0jnIvXhg8xBQDDVnAoMbYhUWiwUtlj4vTA
% https://www.sciencedirect.com/science/article/pii/S1053811918305238?casa_token=xSH5EIN1rZYAAAAA:R2Zf9Lu_np3v0t5-lNZNal0JaJLk1JyYe4QxtmHnba9_lMGJUJgKNK4lHoybuITemQqYUIcuNA
% https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3174820/
% https://www.sciencedirect.com/science/article/pii/S0896627314004000
% https://www.pnas.org/doi/abs/10.1073/pnas.0905267106
% https://www.sciencedirect.com/science/article/pii/S0896627318302411
% https://www.liebertpub.com/doi/full/10.1089/brain.2011.0068
% https://www.sciencedirect.com/science/article/pii/S1053811917302872#f0015
% https://www.sciencedirect.com/science/article/abs/pii/S1053811919303027
% https://pubmed.ncbi.nlm.nih.gov/34625348/

If brain activity patterns contain rich task-relevant information, we should be
able to use the activity patterns to accurately differentiate between different
aspects of the task~\citep[e.g., using pattern classifiers;][]{NormEtal06b}.
For example, prior work has shown a direct correspondence between
classification accuracy and the information content of a signal~\citep{Alva02}.
If brain activity patterns are
